Knowing your role: Varying expectations in software organizations

### 2011-09-28 expectationPeopleTable.tex
Some revisions to Findings section.
Third draft, expectations table.

&Write customization (or script) code& \0&\0&\0\0&\0\0&\0\0\2&\0\0&\0\0\0\2\0\0&\0\0&\0\0\0&\0&\0\0\0&\1&\0\0&\0&\0\2\0\0&\0\0\\

@@

& Write Build Code and prepare a release&\0&\0&\0\0&\0\0&\0\0\0&\1\0&\0\0\0\0\0\0&\0\0&\0\0\2&\0&\0\0\0&\0&\0\0&\0&\0\0\0\0&\0\0\\
& Write experimental (or exploratory) code&\0&\0&\1\2&\0\2&\0\0\0&\0\0&\0\0\0\0\2\0&\1\0&\0\0\0&\0&\0\0\0&\0&\0\0&\0&\0\0\0\0&\0\0\\

@@

@@

@@

& Set roadmap for system (prioritize requirements)&\1&\0&\1\0&\0\1&\1\0\0&\2\0&\0\0\0\0\0\0&\0\0&\0\0\0&\0&\0\2\2&\2&\0\0&\0&\0\0\0\0&\2\1\\
& Provide domain context to non-domain experts (user proxy)&\0&\0&\0\0&\0\0&\0\0\0&\0\0&\0\0\0\0\0\0&\0\0&\0\0\0&\0&\0\2\0&\2&\0\0&\0&\0\2\0\2&\2\0\\

@@

& Provide guidance (mentorship) to newcomers on technical issues&\0&\0&\1\0&\0\0&\0\0\2&\2\2&\2\0\0\0\0\0&\0\1&\0\0\0&\0&\0\0\0&\0&\0\0&\0&\0\0\0\0&\0\0\\

@@

& Handle obstacles and interruptions for technical teams (PoC)&\1&\2&\0\0&\0\0&\2\1\1&\0\1&\0\0\0\0\0\0&\0\0&\0\0\0&\2&\0\0\0&\0&\2\2&\2&\0\0\0\0&\0\0\\

@@

@@

& Deal with financial, clerical, or system administration issues&\0&\1&\0\0&\0\0&\0\0\0&\0\0&\0\0\0\0\0\0&\0\0&\0\0\0&\1&\0\0\0&\0&\0\0&\2&\0\0\0\0&\0\0\\

@@

\caption{Assignment of expectations to people in our field sites. This matrix only includes our interviewees in both organizations; about half of the total number of organization members. Interviewees are clustered approximately by labels, despite label variations. Within each label cluster there is a further subdivision by organization (``G'' stands for Gallium, ``C'' for Cobalt). The colouring of each cell is necessarily subjective, but it corresponds to a rough consensus view of the expectations placed on each individual.}

>>>>

&Write customization or script code& \0&\0&\0\0&\0\0&\0\0\2&\0\0&\0\0\0\2\0\0&\0\0&\0\0\0&\0&\0\0\0&\1&\0\0&\0&\0\2\0\0&\0\0\\

@@

@@

& Write build code and prepare a release&\0&\0&\0\0&\0\0&\0\0\0&\1\0&\0\0\0\0\0\0&\0\0&\0\0\2&\2&\0\0\0&\0&\0\0&\0&\0\0\0\0&\0\0\\
& Write experimental or exploratory code&\0&\0&\1\2&\0\2&\0\0\0&\0\0&\0\0\0\0\2\0&\1\0&\0\0\0&\0&\0\0\0&\0&\0\0&\0&\0\0\0\0&\0\0\\

@@

& Prioritize requirements&\1&\0&\1\0&\0\1&\1\0\0&\2\0&\0\0\0\0\0\0&\0\0&\0\0\0&\0&\0\2\2&\2&\0\0&\0&\0\0\0\0&\2\1\\
& Provide context to non-domain experts (user proxy)&\0&\0&\0\0&\0\0&\0\0\0&\0\0&\0\0\0\0\0\0&\0\0&\0\0\0&\0&\0\2\0&\2&\0\0&\0&\0\2\0\2&\2\0\\

@@

@@

& Provide guidance or mentorship on technical issues&\0&\0&\1\0&\0\0&\0\0\2&\2\2&\2\0\0\0\0\0&\0\1&\0\0\0&\0&\0\0\0&\0&\0\0&\0&\0\0\0\0&\0\0\\

@@

& Handle obstacles and interruptions for technical teams&\1&\2&\0\0&\0\0&\2\1\1&\0\1&\0\0\0\0\0\0&\0\0&\0\0\0&\2&\0\0\0&\0&\2\2&\2&\0\0\0\0&\0\0\\

@@

& Deal with financial, clerical, or sysadmin issues&\0&\1&\0\0&\0\0&\0\0\0&\0\0&\0\0\0\0\0\0&\0\0&\0\0\0&\1&\0\0\0&\0&\0\0&\2&\0\0\0\0&\0\0\\

@@

@@

\caption{{\small\label{tableExpectations}Expectation assignments. This table only includes our interviewees, for which we had the most information. They are clustered approximately by labels, despite label variations. Within each label cluster there is a further subdivision by organization (``G'' stands for Gallium, ``C'' for Cobalt). The shading of each cell is subjective, but it corresponds to a rough consensus among all the interviewed.}}
